quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-11-08 paper-quollr.Rmd
Added reference to application section
Corrected figure caption maths

```{r overviewhtml, eval=knitr::is_html_output(), fig.cap="Wireframe model representation of the NLDR layout, lifted and displayed in high-dimensional space. The left panel shows the NLDR layout with a triangular mesh overlay, forming the wireframe structure. This mesh can be lifted into higher dimensions and projected to examine how the geometric structure of the data is preserved. Panels (a1–a4) display different $2\text{-}D$ projections of the lifted wireframe, where the underlying curved sheet structure of the data is more clearly visible. The triangulated mesh highlights how local neighborhoods in the layout correspond to relationships in the high-dimensional space, enabling diagnostics of distortion and preservation across dimensions.", fig.pos='H', layout = "l-page"}

@@

```{r overview, eval=knitr::is_latex_output(), fig.cap="Wireframe model representation of the NLDR layout, lifted and displayed in high-dimensional space. The left panel shows the NLDR layout with a triangular mesh overlay, forming the wireframe structure. This mesh can be lifted into higher dimensions and projected to examine how the geometric structure of the data is preserved. Panels (a1–a4) display different $2\text{-}D$ projections of the lifted wireframe, where the underlying curved sheet structure of the data is more clearly visible. The triangulated mesh highlights how local neighborhoods in the layout correspond to relationships in the high-dimensional space, enabling diagnostics of distortion and preservation across dimensions.", fig.pos='H'}

@@

Limb muscle cells of mice in @tabula2018 are examined. There are $1067$ single cells, with $14997$ gene expressions. Following their pre-processing, different NLDR methods were performed using ten principal components. Figure \@ref(fig:limb-hbe) (b) is the reproduction of the published plot. The question is whether this accurately represents the cluster structure in the data. Our method help to provide a better $2\text{-}D$ layout.

>>>>

```{r overviewhtml, eval=knitr::is_html_output(), fig.cap="Wireframe model representation of the NLDR layout, lifted and displayed in high-dimensional space. The left panel shows the NLDR layout with a triangular mesh overlay, forming the wireframe structure. This mesh can be lifted into higher dimensions and projected to examine how the geometric structure of the data is preserved. Panels (a1–a4) display different $2\\text{-}D$ projections of the lifted wireframe, where the underlying curved sheet structure of the data is more clearly visible. The triangulated mesh highlights how local neighborhoods in the layout correspond to relationships in the high-dimensional space, enabling diagnostics of distortion and preservation across dimensions.", fig.pos='H', layout = "l-page"}

@@

```{r overview, eval=knitr::is_latex_output(), fig.cap="Wireframe model representation of the NLDR layout, lifted and displayed in high-dimensional space. The left panel shows the NLDR layout with a triangular mesh overlay, forming the wireframe structure. This mesh can be lifted into higher dimensions and projected to examine how the geometric structure of the data is preserved. Panels (a1–a4) display different $2\\text{-}D$ projections of the lifted wireframe, where the underlying curved sheet structure of the data is more clearly visible. The triangulated mesh highlights how local neighborhoods in the layout correspond to relationships in the high-dimensional space, enabling diagnostics of distortion and preservation across dimensions.", fig.pos='H'}

@@

Limb muscle cells of mice in @tabula2018 are examined. There are $1067$ single cells, with $14997$ gene expressions. Following their pre-processing, different NLDR methods were performed using ten principal components. Figure \@ref(fig:limb-hbe) (b) is the reproduction of the published plot. The question is whether this accurately represents the cluster structure in the data. Our method help to provide a better $2\text{-}D$ layout (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:tsne-link-limb), \\@ref(fig:tsne-link-limb-best)"} else { "Figure \\@ref(fig:model-limb)"})`).
